---
title: "My Project"
format: gfm
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dockr

<!-- badges: start -->
<!-- badges: end -->

The goal of dockr is to provide access to the Docker API using only R (no Python, Go or system calls).
The main use case so far is to parse Docker Compose files, pull create and run images and control them.
Not all compose options are implemented yet!

## Installation

You can install the development version of dockr like so:

``` r
remotes::install_github("JBGruber/dockr")
```

## Example

Say you have a Docker Compose file that spins up several containers.
The package includes a very simple one for testing:

```{r example}
readLines(system.file("extdata/docker-compose.yml", package = "dockr")) |> 
  cat()
```

You can start the container defined here by:

```{r}
library(dockr)
compose_up(compose = system.file("extdata/docker-compose.yml", package = "dockr"))
```

To check on your containers, you can use:


```{r}
docker_lc()
```

To stop and remove this container and the underlying image, use:

```{r}
# stop container
docker_stop("test")
# remove container
docker_rmc("test")
# remove image
docker_rmi("redis:alpine")
```

